### 2015-07-01 narrative/data-desc.tex

\subsubsection{Description of Data}

One of the key advantages for a storage system to communicate through objects rather than 
bytes is that it gives a meaning and relationship of certain bytes placed together to form one object.
This permits the system to understand that all of the data in an object needs to be organized together,
and that commonly the entire object will be written and read. Data Models then constitute a collection
of objects which are then placed together via a relationship. In other words, we can think of a
simulation which contains a three dimensional mesh, and that the coordinates of the mesh, along
with the connectivity of the mesh will generally be accessed together. This also us to organize
the data in the storage system in such a way that will allow a user to easily to describe this 
collection of data together, and it will allow the user to describe relationships between the objects
in the data model.

>>>>

\subsubsection{Description of Data}
In order for the middleware and storage layer to understand data,
I/O intentions, and act in a smart way, description of data is needed,
which is achieved by managing data as \textit{objects} in this project.
An object is the smallest unit of data that consists of raw data and metadata,
and a user space variable, such as \textit{temperature}, may consist of a collection
of objects possibly with different accuracy or resolution.
A key advantage of representing data as \textit{objects}, rather than 
bytes, is that it allows data semantics, user intentions, QoS requirements, and
the relationship between user data to be readily captured and embedded with the 
raw data. As an example, retrieving a 3D field generated from a simulation and visualizing it
requires the coordinates and connectivity data 1) to be accessed together 2) with low
latency. This description of data, as enabled by managing data as objects, bridges 
the semantics gap between applictions, middleware, and storage systems,
and allows the system to understand user-level data, execute QoS requirements and policies, and
optimize application and system performance.

Data models then constitute a collection
of objects which are then placed together via a relationship. In other words, we can think of a
simulation which contains a three dimensional mesh, and that the coordinates of the mesh, along
with the connectivity of the mesh will generally be accessed together. This also us to organize
the data in the storage system in such a way that will allow a user to easily to describe this 
collection of data together, and it will allow the user to describe relationships between the objects
in the data model.
